Threat detection in online discussions

### 2016-03-31 submission.tex
endringer i seksjon 4

\section{Previous work}
\label{sec:prev}
There is little previous work specifically devoted to the detection of threats of violence in text. However, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.

@@

\section{The YouTube threat corpus}
\label{sec:data}
The YouTube threat corpus comprises user-written comments from eight different YouTube videos \cite{hammer2014}. The videos cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc. \cite{hammer2014}. 
%The videos cover slightly different topics, the videos all contain the same
%type of discussions, namely of xenophobia and racism. 
A given comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not. The corpus also records the username
%% \footnote{In 2013, YouTube changed its
%%   commenting system from using unique usernames, to using "real
%%   names", like Facebook and other sites \cite{youtube2013}. Some
%%   accounts, however, did not provide real names, so they continue to
%%   only be identified by their usernames.}
  of the comment author.

@@

%to-do: should we anonymize the user names?
Figure~\ref{fig:comments} provides some examples of comments containing \tovs{} taken from the corpus. The first line is the annonymized username, and the subsequent lines are the sentences of the comment. %% An empty line indicates the end of a comment.
The sentences are annotated with a number indicating whether they contain a \tov{} (1) or not (0).

@@

The approach followed in the current paper is to train a machine-learned model to automatically detect threaths, experimenting with a range of different sources of linguistic information for defining our feature templates. 
We also generalize these features through a `backoff' technique. Throughout, we make use of resources and tools that are freely available and reusable.

@@

\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the corpus has been manually split into sentences as part of the annotation process.  We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the SpaCy toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example dependency graph from the corpus. The corpus was further enriched with the cluster labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a corpus containing Reuters English newswire text.
%, with approximately 63 million words and 3.3 million sentences.
We vary the number of clusters to be either 100, 320, 1000 or 3200 clusters and use the full cluster label.  We also make use of the WordNet resource \cite{wordnet} to determine a word's synset, parent and grandparent synset.

@@

We test three different classifiers in our development testing; a Maximum Entropy (MaxEnt) classifier, a Support Vector Machine (SVM), and a Random Forest classifier (RF).  We approach the task as a binary classification task, and we use scikit-learn \cite{scikit-learn} for our classification.

\paragraph{Tuning}
When tuning each model, we aim to maximize the F-score of the model. In the MaxEnt classifier and SVM we tune the C-value, which for both classifiers is the inverse of regularization strength. When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with ever-decreasing increments, with the range of C-values centered on the best performing C-value thus far. After 6 iterations, we terminate the tuning, and select the best performing C-value. When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set). In the following experiments, we perform tuning on all feature sets.

@@

\paragraph{Features}
Based on the enriched corpus, as described above, we experiment with the following feature types:

@@

We use a simple count-based feature reduction on the features in each feature set, where we include in the feature set only the features the appear at least twice in the training data.

>>>>

\section{Related work}
\label{sec:prev}
There is little previous work specifically devoted to the detection of threats of violence in text. However, there is previous work which examines other types of closely related phenomena, such as cyberbullying and hate-speech.

@@

\section{The YouTube threat corpus}
\label{sec:data}
The YouTube threat corpus\footnote{Please contact the authors if you want to obtain access to the corpus for your own research.} comprises user-written comments from eight different YouTube videos \cite{hammer2014}. The videos cover religious and political topics like halal slaughter, immigration, Anders Behring Breivik, Jihad, etc. 
%The videos cover slightly different topics, the videos all contain the same
%type of discussions, namely of xenophobia and racism. 
A given comment consists of a set of sentences, each of them manually annotated to be either a \tov{} (or support for a \tov{}), or not. The corpus also records usernames of the commenters.
%% \footnote{In 2013, YouTube changed its
%%   commenting system from using unique usernames, to using "real
%%   names", like Facebook and other sites \cite{youtube2013}. Some
%%   accounts, however, did not provide real names, so they continue to
%%   only be identified by their usernames.}

@@

%to-do: should we anonymize the user names?
Figure~\ref{fig:comments} provides some examples of comments from the corpus. The first line is the annonymized username, and the subsequent lines are the sentences of the comment. %% An empty line indicates the end of a comment.
The sentences are annotated with a number indicating whether they contain a \tov{} (1) or not (0).

@@

The approach followed in the current paper is to train a machine-learned model to automatically detect threaths. We experiment with a range of different sources of linguistic information for defining our feature templates. 
We also generalize these features through a `backoff' technique. Throughout, we make use of resources and tools that are freely available and reusable.

@@

\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the corpus has been manually split into sentences as part of the annotation process.  We performed tokenization, lemmatization, PoS-tagging and dependency parsing using the spaCy NLP toolkit. SpaCy assigns both the standard Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The dependency parser assigns an analysis in compliance with the ClearNLP converter \cite{Cho:Pal:12}, see Figure~\ref{fig:dep} for an example dependency graph from the corpus. The corpus was further enriched with the cluster labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced from the Reuters corpus of English newswire text (RCV1).
%, with approximately 63 million words and 3.3 million sentences.
We vary the number of clusters to be either 100, 320, 1000 or 3200 clusters and use the full cluster label.  We also make use of the WordNet resource \cite{wordnet} to include information about the synset of a word, as well as its parent and grandparent synsets.

@@

We test three different classification frameworks in our development testing: Maximum Entropy (MaxEnt), Support Vector Machines (SVM), and Random Forests (RF).  We approach the task as a binary classification task, using the implementations found in the scikit-learn toolkit \cite{scikit-learn}.

\paragraph{Tuning}
When tuning each model, we aim to maximize the F-score. For the MaxEnt and SVM classifiers we tune the regularization parameter (C), where a smaller value corresponds to stronger regularization. When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with decreasing increments, with the range of C-values centered on the best performing C-value thus far. After 6 iterations, we terminate the tuning, and select the best performing C-value. When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model), and the number of trees (10, 100 or 1000, depending on the size of the feature set). In the following experiments, we perform tuning on all feature sets.

@@

\paragraph{Features}
Based on the enriched corpus, as described above, we experiment with the following sources of information for defining our features:

@@

We impose a simple count-based reduction of the feature set; only features appearing at least twice in the training data are included in the model.
